---
title: "Problem set 1"
author: "YOUR NAME HERE"
date: "DATE HERE"
---

# Details

- Who did you collaborate with: xxxxx
- Approximately how much time did you spend on this problem set: xxxxx
- What, if anything, gave you the most trouble: xxxx

## Instructions

For this problem set, you'll have three possible things to do.

- "**Question #:**" / "xxxxx" = Write your response to each question by replacing the "xxxx. 1-2 sentences is fine.

- "**Code**" = Write R code in the chunk corresponding to the instructions.

- "**Google**" = Google (or use a different search engine of your choice) the answer to this question.

# Task 1

Answer the following questions about RMarkdown from the short lessons.

## Question 1:

What three (3) characters start and end the YAML information for an RMarkdown file?

xxxxx

## Question 2:

What does the code chunk parameter `echo = FALSE` do?

xxxxx

## Question 3:

How do you change the output type for an RMarkdown file?

xxxxx


# Task 2

## Exploratory Data Analysis

**Code**: load the `tidyverse` package.

```{r load-packages}
# make sure you have tidyverse already installed! (hint: install.packages())

```

### Question 4:

What packages are loaded when you load `tidyverse`?

xxxxx

**Code**: read in the `rickmorty_char.csv` file and assign it to `rm_df`.

```{r load-data-1}
# load in the file './data/rickmorty_char.csv' and assign it to rm_df
# hint: use the read_csv function from the readr (tidyverse) package
```

**Code**: Run `nrow()` and `ncol()` on the data to determine the number of rows and columns of the data frame.

```{r row-col}
# run nrow() and ncol()
```

### Question 4:

How many rows and columns does the data frame include?

xxxxx

**Code**: Run the `glimpse()` function on the data to explore the column formats.

```{r glimpse}
# run the glimpse() function
```

### Question 5:

Which column appears to have missing data (as represented as "" for some values)?

xxxxx

**Code**: Run the `head()` function. Change the parameter `n` to equal 10.

```{r head, eval=F}
head(rm_df, n = 10)
```


## Character Species

Let's try to understand the range of character species in the show.

**Code**: Using `dplyr` and piping (`%>%`), count the number of characters by species and assign it to the dataframe `species_count`. After running it, print it to the console by simply writing the name of the data frame.

```{r species-count-1, eval=F}
# hint: assign species_count through a group_by and summarise
# name your count variable `count` - if you don't you'll get an 
species_count <- rm_df %>%
  group_by(species) %>%
  summarise(count=n())

# print to console by simply writing species_count
species_count
```

### Question 6:

How many [Cronenberg](https://rickandmorty.fandom.com/wiki/Cronenbergs)] characters are in  the show?

xxxxx

**Code**: Create a bar chart with `geom_col()` and choosing the aesthetics mappings as `species` for `x` and `count` for `y`.

```{r species-count-2, eval=F}
species_count %>%
  ggplot(aes(x = species, y = count)) +
  geom_col()
```

As you may notice, there are multiple problems with this plot like: 

- catgories (species) are not ordered;

- labels on the x-axis are difficult to read.

Let's address these problems.

## Re-design our plot

First, let's reorder the categories. To do this, we need to convert the `species` field to a factor. 

**Code**: Rerun the `geom_col()` function by converting `species` to a factor and using the `forcats` funtion `fct_reorder()`:

Hint: to learn how to use `fct_reorder()`, read [this chapter of R4DS](https://r4ds.had.co.nz/factors.html#modifying-factor-order).

```{r species-count-3, eval=F}
library(forcats) # to use the fct_reorder function

# convert species to a factor using the mutate function
# then use fct_reorder to reorder species by the count field
species_count %>%
  mutate(species = factor(species)) %>%
  ggplot(aes(x = fct_reorder(species, count), y = count)) +
  geom_col()
```

Next, let's flip the coordinates. This is where `ggplot2` shines. It's one simple function.

**Google**: Search online (google or another search engine) for what `ggplot2` function will flip the coordinates. 

### Question 7:

What are three words you used to search?

xxxxx

**Code**: Rerun the plot with the coordinates flipped (y axis is character label, x axis is the number of characters).

```{r eval=F}
# coord_flip
species_count %>%
  mutate(species = factor(species)) %>%
  ggplot(aes(x = forcats::fct_reorder(species, count), y = count)) +
  geom_col() +
  coord_flip()
```

Next, let's put labels into our plot. For this, we'll use the `labs()` function, which is an additional layer we can add to our plot.

**Code**: Add the `labs()` function with the following four arguments:

* `x = ""`
* `y = ""`
* `title = "Rick and Morty Characters"`,
* `subtitle = "Number of Characters by Species"`

```{r eval=F}
species_count %>%
  mutate(species = factor(species)) %>%
  ggplot(aes(x = forcats::fct_reorder(species, count), y = count, fill = species)) +
  geom_col() +
  coord_flip() +
  labs(x = "", 
       y = "",
       title = "Rick and Morty Characters",
       subtitle = "Number of Characters by Species"
  )
```

Let's save this plot as a new R object called `g`. For this, you'll simply assign the function to `g`. But note, when you do this, the plot won't automatically run. Therefore, you'll need to call `g` on its own to run the plot.

**Code**: Assign the ggplot from the previous part to `g` and then run `g` on its within the chunk.

```{r eval=F}
# assign plot to g
g <- species_count %>%
  mutate(species = factor(species)) %>%
  ggplot(aes(x = forcats::fct_reorder(species, count), y = count, fill = species)) +
  geom_col() +
  coord_flip() +
  labs(x = "", 
       y = "",
       title = "Rick and Morty Characters",
       subtitle = "Number of Characters by Species"
  )

# simply put "g" to view the plot
g
```

Last, by default, `ggplot2` will use its generic list of colors. However, let's replace the color palette with a palette unique to Rick and Morty.

For this, we'll need to install an additional R CRAN library called `ggsci`.

First, you'll need to install the `ggsci` package.

```{r eval=F}
# install the ggsci package
#install.packages('ggsci')
# create a vector called rm_colors using ggsci::pal_rickandmorty("schifty")(12)
rm_colors = ggsci::pal_rickandmorty("schwifty")(12)

# using g from the previous chunk, add in 
g + scale_fill_manual(values=rm_colors)
```

Next, since we're 

```{r}
g +
  scale_fill_manual(values=rm_colors) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    panel.grid.major.x = element_line(color = "white"),
    panel.ontop = TRUE,
    legend.position = "none"
  ) + 
  scale_y_continuous(position = "bottom") +
  scale_fill_manual(values=rm_colors)
```

### Question 8:

When is it easier to assign a ggplot object to a unique object (e.g., like `g` instead of running the entire plot)?

xxxxx


Finally, we'll need to save this ggplot to a file.


```{r eval=F}
#devtools::install_github("clauswilke/ggtext")
library(ggtext)

getImage <- function(url, species){
  paste0("<img src='",url,"'\n width = '100' /><br>*",species,"*")
}

samp <- char %>%
  group_by(species) %>%
  sample_n(size = 1) %>%
  select(image, species) %>%
  ungroup() %>%
  mutate(link = getImage(image, species))

labels = as.character(samp$link)
names(labels) = samp$species

g +
  theme_minimal() +
  scale_x_discrete(
    name = NULL,
    labels = labels
  ) +
  scale_y_continuous(position = "bottom") +
  scale_fill_manual(values=rm_colors) +
  theme(
    panel.grid = element_blank(),
    panel.grid.major.x = element_line(color = "white"),
    panel.ontop = TRUE,
    legend.position = "none",
    axis.text.x = element_markdown(color = "black", size = 11)
  ) 
```


