---
title: "Text-as-Data"
date: "2019-03-18"
citeproc: false
bibliography: ../../static/bib/references.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    template: ../../pandoc/toc-title_html.template
    toc: true
editor_options: 
  chunk_output_type: console
---

# Tweet of the day

<blockquote class="twitter-tweet" data-conversation="none" data-lang="en"><p lang="en" dir="ltr">Text mining: I really like the tidytext book by <a href="https://twitter.com/juliasilge?ref_src=twsrc%5Etfw">@juliasilge</a> and <a href="https://twitter.com/drob?ref_src=twsrc%5Etfw">@drob</a>: <a href="https://t.co/zgoHq5jr5v">https://t.co/zgoHq5jr5v</a>. And I&#39;m increasingly convinced the single best and most comprehensive resource is <a href="https://twitter.com/kenbenoit?ref_src=twsrc%5Etfw">@kenbenoit</a>&#39;s quanteda: <a href="https://t.co/aVc3N4BCA5">https://t.co/aVc3N4BCA5</a>. It&#39;s tutorials are esp great: <a href="https://t.co/XB5km9OAZm">https://t.co/XB5km9OAZm</a></p>&mdash; Mike Kearney📊 (@kearneymw) <a href="https://twitter.com/kearneymw/status/991861570174058497?ref_src=twsrc%5Etfw">May 3, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>^[[Mike Kearney](https://mikewk.com/) is an assistant professor of Journalism at the University of Missouri and the author of the [`rtweet`](https://rtweet.info/) package to pull Twitter data in RStudio.]


# Slides:

[full screen](../../slides/08-class.html#1) / [pdf version](https://github.com/wesslen/dsba5122-spring2019/raw/master/public/files/dsba5122-spring2019-08-class.pdf)

```{r echo=FALSE}
knitr::include_url('../../slides/08-class.html#1')
```

- <i class="fas fa-book"></i> Julia Silge and David Robinson, ["Tidy Text Mining"](https://www.tidytextmining.com/)

- <i class="fas fa-external-link-square-alt"></i> Ken Benoit and the Quanteda Institute, ["quanteda: Quantitative Analysis of Textual Data"](https://quanteda.io/)

- <i class="fas fa-external-link-square-alt"></i> University of Koblanz, ["Workshop on Topic modeling"](http://topicmodels.west.uni-koblenz.de/#toolbox)

- <i class="fas fa-external-link-square-alt"></i> Matthew Gentzkow, Bryan T. Kelly, and Matt Taddy, ["Text-as-Data"](https://web.stanford.edu/~gentzkow/research/text-as-data.pdf)

# Lab

[full screen](../../slides/08-lab.html#1) / [pdf version](https://github.com/wesslen/dsba5122-spring2019/raw/master/public/files/dsba5122-spring2019-08-lab.pdf)

```{r echo=FALSE}
knitr::include_url('../../slides/08-lab.html#1')
```

RStudio Cloud project for [sample Shiny apps](https://rstudio.cloud/spaces/7976/project/256282)
