---
title: "Quiz 1"
date: "2019-02-04"
due_date: "2019-02-04"
due_time: "11:59 PM"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Name: _____________________

Student ID: _________________________

This quiz is closed-note. You will have 10 minutes to complete.


## Question 1

What are the three disciplines of data visualizations?

A) Information graphics, scientific graphics, graphic analytics

B) Grammar of graphics, exploratory analysis, confirmatory analysis

C) Information visualization, visual analytics, scientific visualization

D) Computer graphics, human-computer interaction, spatial mapping

## Question 2

According to "The Truthful Art", the five qualities of a great visualization are:

A) Truthful, functional, beautiful, insightful, enlightening

B) Labeled, framed, attractive, clear, correct

C) Intuitive, functional, clear, enlightening, correct

D) Truthful, framed, attractive, beautiful, insightful

## Question 3

According to "The Truthful Art", which perceptual task (or channel) enables the most accurate estimates:

A) Area

B) Shading

C) Color/Hue

D) Position along a common axis

##  Use this dataset for Question 4 and 5

```{r}
head(mpg, n = 5)
```

## Question 4

Which code produces the **average** `mpg` and **count** for **Volkswagen** manufactured cars by the car's cylinder (`cyl`):

```{r echo=FALSE}
mpg %>%
  filter(manufacturer == "volkswagen") %>%
  group_by(cyl) %>%
  summarise(avgHwy=mean(hwy), count=n())
```

A)

```{r eval=FALSE}
mpg %>%
  filter(manufacturer == "volkswagen") %>%
  group_by(cyl) %>%
  summarise(avgHwy=mean(hwy), count=n())
```

B)

```{r eval=FALSE}
mpg %>%
  where(manufacturer == "volkswagen") %>%
  select(cyl) %>%
  summarise(avgHwy=mean(hwy), count=n())
```

C)

```{r eval=FALSE}
mpg %>%
  group_by(cyl) %>%
  summarise(avgHwy=mean(hwy), count=n()) %>%
  filter(manufacturer == "volkswagen")
```

D)

```{r eval=FALSE}
mpg ->
  group_by(cyl) ->
  average(avgHwy=m(hwy)) ->
  count(count=n()) ->
  filter(manufacturer == "volkswagen")  
```

## Question 5

What code replicates this plot:

```{r echo=FALSE,fig.height=4,fig.width=5}
ggplot(mpg, aes(x = cty, y = hwy, color = class)) +
  geom_point() +
  facet_wrap(year~.) +
  theme_bw() +
  theme(legend.position = "bottom")
```


A)

```{r eval=FALSE}
ggplot(mpg, aes(x = cty, y = hwy, color = class)) +
  geom_point() +
  facet_grid(year~.)
```

B)

```{r eval=FALSE}
ggplot(mpg, aes(x = cty, y = hwy, color = class)) +
  geom_scatter() +
  facet_wrap(year~.) +
  theme(legend.position = "bottom")
```

C)

```{r eval=FALSE}
ggplot(mpg, aes(x = cty, y = hwy, color = class)) +
  geom_point(year) +
  theme_bw(legend.position = "bottom") +
  coords(facet_grid)
```

D)

```{r eval=FALSE}
ggplot(mpg, aes(x = cty, y = hwy, color = class)) +
  geom_point() +
  facet_wrap(year~.) +
  theme_bw() +
  theme(legend.position = "bottom")
```
