---
title: "Quiz 2"
date: "2019-02-25"
due_date: "2019-02-25"
due_time: "11:59 PM"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(tidyverse); library(ggridges); library(ggthemes)
library(maps)
crimes <- USArrests %>%
  rownames_to_column(var = "state") %>%
  mutate(state = tolower(state)) %>%
  gather("variable","value",-state)

states_map <- map_data("state")

urbanPop <- crimes %>%
  filter(variable == "UrbanPop") 

l <- c("Jan 2013","Feb 2013","Mar 2013","Apr 2013",
       "May 2013", "Jun 2013", "Jul 2013", "Aug 2013",
       "Sep 2013", "Oct 2013", "Nov 2013", "Dec 2013")

jfkWeather <- filter(nycflights13::weather, origin == "JFK") %>%
  mutate(month = format(as.Date(time_hour), format = "%b %Y")) %>%
  select(month, day, hour, temp, dewp, humid, wind_dir, wind_speed, precip) %>%
  mutate(month = factor(month, levels = l))
```

Name: _____________________

Student ID: _________________________

This quiz is closed-note. You will have 10 minutes to complete.


## Question 1

According to Cairo's "The Truthful Art", time series variables can decomposed into what three components?

A) Auto regressive, moving average, and integration (ARIMA)

B) Trend, seasonality, and noise

C) Principal components, Kalman filter, recurrent neural networks

D) Cyclical, short term, and long term

## Question 2

According to Cairo's "The Truthful Art", what are the three main components of maps:

A) Scales, projections, and symbols

B) Polygons, edges, and labels

C) Density, spatial, and temporal

D) Borders, grids, and regions

##  Use this dataset for Questions 3, 4 and 5

This dataset includes hourly weather updates for New York City's JFK airport for 2013.

```{r}
head(jfkWeather, n = 5)
```

We will use two libraries.

```{r eval=FALSE}
library(tidyverse)
library(ggridges)
```


## Question 3

Which code produces this plot:

```{r echo=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, fill = month)) +
  geom_density(alpha = 0.4)
```

A)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(x = temp, y = density, fill = month) +
  geom_density(alpha = 0.4)
```

B)

```{r eval=FALSE}
ggplot(jfkWeather, aes(x = temp, y = density, color = month)) +
  geom_distribution(alpha = 0.4)
```

C)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, fill = month)) +
  geom_density(alpha = 0.4)
```

D)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, color = month)) +
  geom_kernel(alpha = 0.4)
```

## Question 4

Which code (using `ggridges`) produces this plot:

```{r echo=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, y = month, fill = month)) +
  geom_density_ridges(alpha = 0.4) + 
  theme_bw() +
  theme(legend.position = "none")
```

A)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, y = month, color = month)) +
  geom_density(alpha = 0.4) + 
  theme_bw() +
  theme(legend.position = "none")
```

B)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, y = month, fill = month)) +
  geom_kernel(adjust = 0.4) + 
  theme_bw(legend.position = "none")
```

C)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(x = temp, y = year, color = year) +
  geom_density(adjust = 0.4) + 
  theme_bw() +
  theme(legend.position = "none")
```

D)

```{r eval=FALSE}
jfkWeather %>%
  ggplot(aes(x = temp, y = month, fill = month)) +
  geom_density_ridges(alpha = 0.4) + 
  theme_bw() +
  theme(legend.position = "none")
```

## Question 5

The following plot provides the average hourly temperature at JFK airport for Jan - Mar 2013 with bootstrapped 95 percent confidence intervals using error bars.

```{r echo=TRUE,fig.height=3,fig.width=6}
jfkWeather %>%
  filter(month %in% c("Jan 2013","Feb 2013","Mar 2013")) %>%
  ggplot(aes(x = month, y = temp)) +
  stat_summary(fun.y = mean, geom = "point") + 
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", fun.args=list(conf.int = .95) ) + 
  theme_bw() +
  coord_flip() +
  scale_y_continuous(breaks= seq(32,40,by=0.5)) +
  labs(x = " ", y = "Hourly Temperature")
```

What is the correct interpretation of the bootstrapped confidence intervals in this plot?

A) After resampling with replacement, the mean hourly temperature per month is within the upper and lower limits in 95 percent of the resamples.

B) We expect that the hourly temperature for JFK per month will be within the upper and lower limits 95 percent of observations.

C) 95 percent of the temperature observations (on an hourly) are within the upper and lower limits.

D) Assuming a normal distribution, we expect the temperature in each month to be within the upper and lower limits 95 percent of the time.
` 
