---
title: "Quiz 4"
date: "2019-04-08"
due_date: "2019-04-08"
due_time: "11:59 PM"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

Name: _____________________

Student ID: _________________________

This quiz is closed-note. You will have 10 minutes to complete.

## Question 1

In a network (or graph), individual data instances (e.g., records/observations) are represented by ____[A]____ while ____[B]____ represent relationships between those instances.

A) [A] = edges, [B] = vertices/nodes

B) [A] = kernels, [B] = mappings

C) [A] = vertices/nodes, [B] = edges

D) [A] = rows, [B] = mappings

## Question 2

All of the following are ways to represent networks as data **except**:

A) Edge list

B) Transformation matrix

C) Adjacency matrix

D) Adjacency list

## For questions 3-4, use this shiny code to fill in the [A] and [B] blanks:

```{r eval=F}
library(shiny)

ui <- fluidPage(
  sliderInput(inputId = "num",
              label = "Choose a number",
              value = 25, min = 1, max = 100),
  plotOutput("hist")
)

server <- function(input, output) {

  data <- reactive({
    rnorm(___A___)
  })

  output$hist <- renderPlot({
    hist(___B___)
  })
  
}

shinyApp(ui = ui, server = server)
```


## Question 3

What should be in place of "___A___" to call the `num` slider object from the UI?

A) `num`

B) `input$num`

C) `"num"`

D) `ui$num`

## Question 4

What should be in place of "___B___" to call the reactive object `data`?

A) `data`

B) `reactive$data`

C) `data()`

D) `output$data`

## Question 5

In shiny, what function helps debugging by allowing you to set a breakpoint anywhere in your code?

A) `server()` function

B) `checkpoint()` function

C) `diagnose()` function

D) `browser()` function
