---
title: "Quiz 5"
date: "2019-04-22"
due_date: "2019-04-22"
due_time: "11:59 PM"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

Name: _____________________

Student ID: _________________________

This quiz is closed-note. You will have 10 minutes to complete.

## Question 1

If your Shiny App is taking a long time to load initially, what could you do to improve your run time?

A) Remove slow pre-processing steps by loading post-processing flat file(s) (e.g., .csv, .rds) instead.

B) Remove all libraries from your Shiny App.

C) Run your Shiny app as a `flexdashboard` or `shinydashboard` app.

D) Run your Shiny app from the command line instead of RStudio.

## Question 2

The `profvis` package enables R programmers to:

A) visualize the reactive links between Shiny inputs and outputs.

B) save what packages are used in an R script.

C) view what geoms are available in ggplot2.

D) identify what part of their code is slowest to run in R.

## Question 3

In Shiny, plot caching is when we temporarily save a copy of a plot called (e.g., ggplot2). Which situation will improve Shiny performance (faster updates) if we use plot caching?

A) If the Shiny App is connected to a database. 

B) If we expect many users to view similar plots many times.

C) If the Shiny App has many ggplot2 graphs that are rarely used.

D) If the Shiny App includes many `htmlwidget` packages.

## For questions 4-5, use this Shiny code:

```{r eval=F}
library(shiny)

ui <- fluidPage(
  sliderInput(inputId = "num",
              label = "Choose a number",
              value = 25, min = 1, max = 100),
  plotOutput("hist"),
  printOutput("plot_click_info")
)

server <- function(input, output) {

  output$hist <- renderPlot({
    hist(rnorm(input$num))
  })
  
  output$plot_clickinfo <- renderPrint({
    str(___[A]___) # str() converts obj. to a string
  })
  
}

shinyApp(ui = ui, server = server)
```

## Question 4

How could we track where the user clicked in the plot `hist`?

A) Add in the `plotOutput()` the `click =` parameter with a unique object name (e.g., "plot_click").

B) Add in a `plotClick(hist)` function as an output in our server.

C) Add in a `plot_click(hist)` function as an output in our server.

D) Add in the `hist()` the `click =` parameter with a unique object name (e.g., "plot_click").

## Question 5

If we called our click object "plot_click" in Question 4, how would we call it in [A]?

A) `output$plot_click`

B) `input$plot_click`

C) `plot_click`

D) `hist$plot_click`
